\documentclass[margin, 10pt]{res}
\usepackage{helvet}
\setlength{\textwidth}{5.1in}

\begin{document}

\moveleft.5\hoffset\centerline{\large\bf Kan Ouivirach}
\vspace{2mm}
\moveleft.5\hoffset\centerline{{\tt zkan@hey.com}}
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip

\moveleft.5\hoffset\centerline{7/86 Moo 2 Bangpood Pakkret Nonthaburi 11120}
\moveleft.5\hoffset\centerline{+66-83-749-5568}

\begin{resume}

\section{Profile}

7+ years experience in software development and data platform,
from engineer to manager. Passionate in software engineering,
data engineering, and data science.

\section{Current Position}

{\bf Data Craftsman and Technical Coach, ODDS}\\
{\it \small Apr 2020 -- Present}\\
Help enterprises build a data platform and creating a data-informed
culture in a way that empowers people to answer their own questions
and make decisions based on findings.

Act as a technical coach on projects, especially ones that require
research and data analysis from a software development perspective.
Develop, test, and maintain highly scalable data architectures
to keep data accessible and ready for analysis. Build high-performance
algorithms, prototypes, predictive models and proof of concepts.
Research opportunities for data acquisition and new uses for
existing data. Recommend ways to improve data reliability, efficiency,
and quality.

Teach the following hands-on workshops for the ODDS team and career switchers.

\begin{itemize}
  \item React from Beginner to Advanced
  \item Data Pipelines with Airflow
  \item Kafka 101
  \item Python \& Django for Web Development
\end{itemize}

\section{Experience}

{\bf Software Engineer Manager, Pronto Tools}\\
{\it \small Jul 2019 -- Mar 2020 (9 months)}\\
Take care of all design and architecture. Guide and support a team of
software engineers perform at their best. Act act as liaisons between
the engineering team and other teams within the company.

{\bf Lead Software Architect, Pronto Tools}\\
{\it \small Sep 2017 -- Jun 2019 (1 year 10 months)}\\
Act as a lead on all internal and external projects, especially ones that
require research and data analysis from a software development perspective.
Develop, test, and maintain highly scalable data architectures to keep data
accessible and ready for analysis. Build high-performance algorithms,
prototypes, predictive models and proof of concepts. Research opportunities
for data acquisition and new uses for existing data. Recommend ways to
improve data reliability, efficiency, and quality.

Also, act as a mentor for the software engineering team and interns.

{\bf Research \& Development Engineer, Pronto Marketing}\\
{\it \small May 2013 -- Aug 20217 (4 years 4 months)}\\
Develop, test, and maintain highly scalable architectures.
Research opportunities for innovation. Recommend ways to improve
platform reliability, efficiency, and quality.

Act as a mentor for interns.

{\bf Graduate Teaching Assistant, Asian Institute of Technology}\\
{\it \small Aug 2012 -- Dec 2012 (5 months)}\\
Supervised students, taught lab, and graded work in Web Application Engineering
mainly focusing on Ruby on Rails (around 15 students per class).

{\bf Part-time Lecturer, Bangkok University}\\
{\it \small July 2011 -- April 2012 (10 months)}\\
Taught in Computer and Information Technology (around 50 students per class).

{\bf Graduate Teaching Assistant, Asian Institute of Technology}\\
{\it \small Aug 2009 -- Dec 2009 (5 months)}\\
Supervised students and graded work in Web Application Engineering mainly focusing
on Ruby on Rails (around 15 students per class).

\section{Community \\ Experience}

{\bf Co Lead, Facebook Developer Circle: Bangkok}\\
{\it \small Apr 2019 -- Present}\\
{\tt https://developers.facebook.com/developercircles/}

{\bf Community Organizer, PyLadies Bangkok}\\
{\it \small May 2019 -- Present}\\
{\tt https://pyladies.com/}

{\bf Community Organizer, Data Council Bangkok}\\
{\it \small Dec 2018 -- Present}\\
{\tt https://www.meetup.com/DataCouncil-AI-Bangkok-Data-Engineering-Science/}

{\bf Mentor, Django Girls}\\
{\it \small May 2018}\\
{\tt https://djangogirls.org/}

\section{Selected \\ Certifications}

{\bf Astronomer Certification DAG Authoring for Apache Airflow}\\
{\it \small Astronomer. Issued Aug 2021.}\\
{\tt https://www.credly.com/badges/cc7faa44-a61d-43f0-9131-dfbb47f0b219}

{\bf Astronomer Certification for Apache Airflow Fundamentals}\\
{\it \small Astronomer. Issued Apr 2021.}\\
{\tt https://www.credly.com/badges/39c4a9b5-ac2d-49bf-9e16-695eff2bc3e2}

{\bf Flight Levels Introduction}\\
{\it \small Flight Levels Academy. Issued Dec 2020.}\\
{\tt https://www.flightlevels.io/}

{\bf Flight Levels Flow Design}\\
{\it \small Flight Levels Academy. Issued Nov 2020.}\\
{\tt https://www.flightlevels.io/}

\section{Interests}

Data engineering \& science, and infrastrucutre, Web development,
machine learning, computer vision and image processing.

\section{Technologies}

Python, Django, Go, Node.js, React, JavaScript, Cypress, HTML, CSS,
Java, Spring Boot, HTML, CSS, AWS, Google Cloud, Pulumi, Terraform,
Docker, Kubernetes, Apache Airflow, Apache Spark, Apache Kafka, RDBMS, NoSQL,
Argo CD, Jenkins, Git, Jupyter Notebook

\section{Websites}

Personal Site: {\tt https://www.kanouivirach.com/}\\
Hasnode: {\tt https://zkan.hashnode.dev/}\\
Medium: {\tt https://zkan.medium.com/}\\
DEV Community: {\tt https://dev.to/zkan/}\\

\section{Education}

{\bf Asian Insititute of Technology, Thailand} \\
Ph.D., Computer Science, 2013. \\
{\it Thesis:} Incremental Human Behavior Modeling and Suspicious Activity
Detection.

{\bf Asian Insititute of Technology, Thailand} \\
M.Eng., Computer Science, 2008. \\
{\it Thesis:} Human Behavior Profileing for a Video Surveillance System.

{\bf Kasetsart University, Thailand} \\
B.Eng., Computer Engineering, 2005. \\
{\it Senior Project:} Mining System using Classification based on Multiple
Association Rules (CMAR).

\section{Selected \\ Publications}

Ouivirach, K.\ and Dailey, M.N.\ (2013), Extracting the object from the shadows:
Maximum likelihood object/shadow discrimination. In {\it Proceedings of
ECTI-CON}, 2013. Article number 6559543.

Ouivirach, K., Gharti, S., and Dailey, M.N.\ (2013), Incremental behavior
modeling  and suspicious activity detection. {\it Pattern Recognition}, 46(3):
671--680.

Ouivirach, K., Gharti, S., Dailey, M.N.\ (2012), Automatic suspicious behavior
detection from a small bootstrap set. In {\it International Conference on
Computer Vision Theory and Applications (VISAPP)}, pp.\ 655--658.

Ouivirach, K.\ and Dailey, M.N.\ (2010), Clustering human behaviors with
dynamic time warping and hidden Markov models for a video surveillance system.
{\it Proceedings of ECTI-CON}, 2010, pp.\ 884--888.

\section{Professinal \\ Activities}

Reviewer for International Conference on Electrical Engineering/Electronics,
Computer, Telecommunications and Information Technology (ECTI-CON),
International Symposium on Intelligent Signal Processing and Communication
Systems (ISPACS), Thailand-Japan International Academic Conference (TJIA),
Frontiers of Information Technology (FIT).

Member of IEEE since 2009.

\end{resume}
\end{document}
