\documentclass[margin, 10pt]{res}
\usepackage{helvet}
\setlength{\textwidth}{5.1in}

\begin{document}

\moveleft.5\hoffset\centerline{\large\bf Kan Ouivirach}
\vspace{2mm}
\moveleft.5\hoffset\centerline{{\tt kan@prontomarketing.com}}
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip

\moveleft.5\hoffset\centerline{Pronto Group Ltd.\ (Headquarters)}
\moveleft.5\hoffset\centerline{15 Rajanakarn Bldg., $3^{rd}$, $6^{th}$, and
$7^{th}$ Fl.,}
\moveleft.5\hoffset\centerline{Soi Pradipat 17, Pradipat Rd., Samsennai,}
\moveleft.5\hoffset\centerline{Phayathai, Bangkok 10400}
\moveleft.5\hoffset\centerline{+66-2-278-4319}

\begin{resume}

\section{Current Position}

Lead Software Architect, Pronto Tools

Act as a lead on projects, especially ones that require research and data
analysis from a software development perspective. Develop, test, and maintain
highly scalable data architectures to keep data accessible and ready for
analysis. Build high-performance algorithms, prototypes, predictive models and
proof of concepts. Research opportunities for data acquisition and new uses for
existing data. Recommend ways to improve data reliability, efficiency, and
quality.

\section{Research \\ Interests}

Machine learning, computer vision and image processing especially applied video
surveillance.

\section{Education}

{\bf Asian Insititute of Technology, Thailand} \\
Ph.D., Computer Science, 2013. \\
{\it Thesis:} Incremental Human Behavior Modeling and Suspicious Activity
Detection.

{\bf Asian Insititute of Technology, Thailand} \\
M.Eng., Computer Science, 2008. \\
{\it Thesis:} Human Behavior Profileing for a Video Surveillance System.

{\bf Kasetsart University, Thailand} \\
B.Eng., Computer Engineering, 2005. \\
{\it Senior Project:} Mining System using Classification based on Multiple
Association Rules (CMAR).

\section{Selected \\ Publications}

Ouivirach, K.\ and Dailey, M.N.\ (2013), Extracting the object from the shadows:
Maximum likelihood object/shadow discrimination. In {\it Proceedings of
ECTI-CON}, 2013. Article number 6559543.

Ouivirach, K., Gharti, S., and Dailey, M.N.\ (2013), Incremental behavior
modeling  and suspicious activity detection. {\it Pattern Recognition}, 46(3):
671--680.

Ouivirach, K., Gharti, S., Dailey, M.N.\ (2012), Automatic suspicious behavior
detection from a small bootstrap set. In {\it International Conference on
Computer Vision Theory and Applications (VISAPP)}, pp.\ 655--658.

Ouivirach, K.\ and Dailey, M.N.\ (2010), Clustering human behaviors with
dynamic time warping and hidden Markov models for a video surveillance system.
{\it Proceedings of ECTI-CON}, 2010, pp.\ 884--888.

\section{Professinal \\ Activities}

Reviewer for International Conference on Electrical Engineering/Electronics,
Computer, Telecommunications and Information Technology (ECTI-CON),
International Symposium on Intelligent Signal Processing and Communication
Systems (ISPACS), Thailand-Japan International Academic Conference (TJIA),
Frontiers of Information Technology (FIT).

Member of IEEE since 2009.

\end{resume}
\end{document}
